\documentclass[a4paper, 12pt]{article}
\usepackage{cmap}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{amsmath,amsfonts,amsthm,mathtools}
\usepackage{icomma}
\usepackage{euscript}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{linkcolor}{HTML}{534B4F}
\definecolor{urlcolor}{HTML}{6699CC}
\definecolor{citecolor}{HTML}{FE2712}
\hypersetup{pdfstartview=FitH,  linkcolor=linkcolor,urlcolor=urlcolor,citecolor=citecolor, colorlinks=true}
\author{Andrey Volkov Alexandrovich}
\title{Java Android Developer}
\date{\today}

\begin{document}
	\selectlanguage{english}
	\rm
	\maketitle
	
	\part{How to connect with me}
	\bf
	\begin{enumerate}
		\item Phone(8(916)221-26-40).(Otherwise you can use it to connect with me via Telegram, WhatsApp and etc.).
		\item E-mail(ballgameandrew@yandex.ru)
		\item \href{https://vk.com/andrey_vlk}{VK}
		\item \href{https://www.linkedin.com/in/andre-volkov-v/}{LinkedIn}
		\item \href{https://javarush.ru/users/2482341}{JavaRush}
	\end{enumerate}
	\rm
	
	\part{Skills}
	\section*{Hard Skills}
	\subsection*{Programming languages}
	\begin{enumerate}
		\item Java (Java Core). (7+ months of work experience)
		\item C++(basics). (3+ months of work experience)
		\item Python(basics). (2+ months of work experience)
	\end{enumerate}
	\subsection*{Other Technical Skills}
	\begin{enumerate}
		\item XML
		\item \LaTeX
		\item HTML(basics)
		\item CSS(basics)
		\item .sh\cite{bashing}(basics)
	\end{enumerate}
	\subsection*{All other skills}
	\begin{enumerate}
		\item English language.($\approx$ (Intermediate\cite{b1} - Upper Intermediate\cite{b2}))
		\item Communication Skills.\cite{team}
	\end{enumerate}

	\part{Links}
	\bf
	\begin{itemize}
		\item \href{https://github.com/AndreyVAAVA}{GitHub}
		\item \href{https://www.linkedin.com/in/andre-volkov-v/}{LinkedIn}
		\item \href{https://www.codewars.com/users/AndreyVAAVA}{CodeWars}
		\item \href{https://javarush.ru/users/2482341}{JavaRush}
		\item \href{https://repl.it/@AndrewVolkov}{Repl.it}
		\item \href{https://habr.com/ru/users/andreyder/}{Habr}
		\item \href{https://stackoverflow.com/users/14551339/the-worst}{StackOverflow}
		\item \href{https://stepik.org/users/308680720}{Stepik}
		\item \href{https://vk.com/andrey_vlk}{VK}
		\item Telegram. (You can find me by my phone number (8(916)221-26-40)
	\end{itemize}
	\rm
	\part{Experience}
	
	\section*{Java}
	\begin{enumerate}
		\item Samsung IT School.($\approx$ 7 month)
		\item JavaRush.($\approx$ 3 month)
		\item Other internet resources.($\approx$ 8 month)
		\item Knowledge of clean code.(Robert Martin)
	\end{enumerate}

	\section*{C++}
	\begin{enumerate}
		\item YouTube(\bf \href{https://www.youtube.com/channel/UCtLKO1Cb2GVNrbU7Fi0pM0w}{\#SimpleCode} \rm channel).(3+ monthes)
		\item HSE Courses(wasn't completed, but I get a lot of new information, that later helped me in C++ and Java).
		\item Children's Technopark MIREA.(4+ monthes)
	\end{enumerate}
	
	\section*{Python}
	\begin{enumerate}
		\item School 2025.(1 year of study, but this could be equlied to $\approx$ 1-2 months of work experience)
		\item Other Internet Resources.(1 month of work experience)
	\end{enumerate}
	
	\section*{.sh}
	\begin{enumerate}
		\item \bf \href{https://wiki.archlinux.org/}{Arch Wiki}\rm.($\approx$ 1 year of work experience, that could be equaled to $\approx$ 1-2 months of work experience)
		\item \bf \href{https://www.youtube.com/channel/UC2eYFnH61tmytImy1mTYvhA}{Luke Smith}\rm.(Basics of: vim configuration, .sh shells customization and basics of DEs\cite{DE}(such as different WMs\cite{WM}))
	\end{enumerate}
	
	\section*{\LaTeX}
	\begin{enumerate}
		\item \bf \href{https://www.youtube.com/channel/UC2eYFnH61tmytImy1mTYvhA}{Luke Smith}\rm.(3+ monthes of work experience)
		\item \bf \href{https://www.overleaf.com/}{Overleaf}\rm.(I still don't have an account. Link Redirects to main page)
	\end{enumerate}

	\part{About me}
	\section*{Dry Information}
	\begin{enumerate}
		\item I was playing(I still play it, but now I spend less time on it) baseball for about 10 years.
		\item I have been learning programming (not only at school) since December 2019.(I must say, thanks to the YouTube channel \href{https://www.youtube.com/channel/UCTW0FUhT0m-Bqg2trTbSs0g}{IT-KAMASUTRA}. This channel given me reasons to learn programming.(he showed that it can be interesting))
		\item I was studying in Children's Technopark MIREA. I am still studying at: Samsung IT School, NTI. (And on courses like CodeGym(JavaRush), Stepik (courses on this platform))
	\end{enumerate}

	\section*{More about me}
	
	17 years old. Programming since 16 years old. Mobile developer. Sometimes I like to play computer games (and sometimes I like to watch how does it works). I love to customize GNU Linux and Windows(Basically installation of WSL2\cite{WSL}). I always prefer to learn something new than nothing. After interview with mobile delveloper\cite{IT-Beard} and after different videos by Yandex I would like to work there.(Especially when I saw on Instagram that you are using your robots in Innopolis (Yandex.Rover)\cite{Rover}. I do not use tobacco or alcoholic products.
	\footnotesize
	\begin{thebibliography}{9}
		\bibitem{bashing}
		Some basic commands.(Such as rm, rmdir, apt install, pacman -Syy and etc.). And .sh means that I can use different .sh shells (Such as .bash, .zsh, .fish and etc.)
		\bibitem{b1}
		\selectlanguage{russian}
		Уровень английского языка \it Intermediate\rm, который обозначается маркировкой B1 согласно общеевропейской компетенции владения иностранным языком, идет следующим после \it Pre-Intermediate\rm. Название этой ступени происходит от слова intermediate, перевод которого — <<средний>>. Так, \bf Intermediate — это так называемый <<средний>> уровень владения языком, позволяющий достаточно свободно разговаривать на английском, обсуждать многие профессиональные и бытовые темы, понимать на слух практически все сказанное на английском языке в обычном темпе.\rm Уровень владения языком B1 позволяет сдавать вступительные экзамены в российские ВУЗы и на подготовительные курсы за рубежом.\href{https://englex.ru/level-intermediate/}{\bf Taken From}
		\bibitem{b2}
		Уровню \it Upper-Intermediate \rm присвоено обозначение B2 согласно общеевропейской компетенции владения иностранным языком (CEFR). Ступень \it Upper-Intermediate \rm — серьезный уровень знаний, достаточный для общения на английском языке почти во всех сферах. Как вы помните, перевод слова \it intermediate \it звучит как <<средний>>, а upper — <<верх>>, поэтому уровень \it Upper-Intermediate \rm означает ступень выше среднего. Люди, занимающиеся английским на уровне \it Upper-Intermediate \rm , могут начинать готовиться к международным экзаменам \it TOEFL \rm или \it IELTS\rm. Сертификаты этих экзаменов пригодятся для поступления в иностранные вузы и трудоустройства за границей, а также для эмиграции.\href{https://englex.ru/level-upper-intermediate}{\bf Taken From}
		\bibitem{team}
		I was woking with some teams. Usually I was one of the co-leaders.
		\bibitem{DE}
		DE - Desktop Environment
		\bibitem{WM}
		WM - Windows Manager
		\bibitem{WSL}
		WSL - Windows Subsystem for Linux.
		\bibitem{IT-Beard}
		\href{https://www.youtube.com/watch?v=j9zlTFLLrSI}{АйТиБорода}
		\bibitem{Rover}
		\href{https://www.instagram.com/p/CIkkBixFaiq/?utm_source=ig_web_copy_link}{Innopolis}. \href{https://www.instagram.com/p/CMCSzacls9b/?utm_source=ig_web_copy_link}{Yandex}
	\end{thebibliography}
\end{document}